SecFFT: Safeguarding Federated Fine-tuning for Large Vision Language Models against Covert Backdoor Attacks in IoRT Networks

### 2024-10-22 response.tex

% [R6] Han S, Buyukates B, Hu Z, et al. FedSecurity: A Benchmark for Attacks and Defenses in Federated Learning and Federated LLMs[C]//Proceedings of the 30th ACM SIGKDD Conference on Knowledge Discovery and Data Mining. 2024: 5070-5081.

% [R7] Liu Z, He W, Chang C H, et al. SPFL: A Self-purified Federated Learning Method Against Poisoning Attacks[J]. IEEE Transactions on Information Forensics and Security, 2024.

% [R8] Wei K, Li J, Ma C, et al. Personalized federated learning with differential privacy and convergence guarantee[J]. IEEE Transactions on Information Forensics and Security, 2023.

% [R9] Ilhan F, Su G, Liu L. Scalefl: Resource-adaptive federated learning with heterogeneous clients[C]//Proceedings of the IEEE/CVF Conference on Computer Vision and Pattern Recognition. 2023: 24532-24541.

% [R10] Wu X, Huang F, Hu Z, et al. Faster adaptive federated learning[C]//Proceedings of the AAAI conference on artificial intelligence. 2023, 37(9): 10379-10387.

% [R11] Ye R, Wang W, Chai J, et al. Openfedllm: Training large language models on decentralized private data via federated learning[C]//Proceedings of the 30th ACM SIGKDD Conference on Knowledge Discovery and Data Mining. 2024: 6137-6147.

% [R12] Nguyen T D, Rieger P, De Viti R, et al. {FLAME}: Taming backdoors in federated learning[C]//31st USENIX Security Symposium (USENIX Security 22). 2022: 1415-1432.

% [R13] Yang H, Xi W, Shen Y, et al. RoseAgg: Robust Defense Against Targeted Collusion Attacks in Federated Learning[J]. IEEE Transactions on Information Forensics and Security, 2024.

% \end{comment}

\end{document}

% FedSecurity: A Benchmark for Attacks and Defenses in Federated Learning and Federated LLMs
% SPFL: A Self-purified Federated Learning Method Against Poisoning Attacks
% Personalized Federated Learning With Differential Privacy and Convergence Guarantee
% ScaleFL: Resource-Adaptive Federated Learning with Heterogeneous Clients
% Faster Adaptive Federated Learning
% FedALA: Adaptive Local Aggregation for Personalized Federated Learning
% OpenFedLLM: Training Large Language Models on Decentralized Private Data via Federated Learning
% Every Parameter Matters: Ensuring the Convergence of Federated Learning with Dynamic Heterogeneous Models Reduction
% FLAME: Taming Backdoors in Federated Learning
% RoseAgg: Robust Defense Against Targeted Collusion Attacks in Federated Learning
